%%--------------------------------------
%% Berlin Brown
%% botlist - ghostnetwork and mulit-language architecture
%% Date: 3/28/2008
%%--------------------------------------

% Use report or article
\documentclass[12pt]{report}

\usepackage{graphicx}
\usepackage{latexsym}
%-----------------------------
\oddsidemargin = .5in
\textwidth = 6in

\headheight = 0in
\headsep = 0in
\topmargin = .25in
\textheight = 8.5in

\floatsep = .29in
\textfloatsep = \floatsep
\intextsep = \floatsep
%-----------------------------

\begin{document}

\title{Botlist Ghost Network - Building a Web Application with a Multi-Language Architecture}

\author{Berlin Brown\\
  Founder of Botnode.com\\
  berlin.brown at gmail.com\\
  Atlanta, Ga\\
  \date{\today}}

\maketitle

%%--------------------------------------
%% Abstract
%%--------------------------------------

\begin{abstract}
This article presents Botlist-Network (Botlist).  Botlist is a 
web application and information retrieval system that aims to collect
and analyze content from the vast world wide web.  Botlist is an specification
for describing the platform, the Botlist web front end and the Botlist backend
infrastructure for crawling and analyzing web documents and converting those
documents into a machine readable format such as RDF semantic web formats.

This article also looks at the use of several powerful open source programming
languages.  Each language is used for it strenghs.
\end{abstract}

%%--------------------------------------
%% Table of Contents
%%--------------------------------------
\tableofcontents

\include{overview}
\include{java}
\include{jruby}
\include{python}
\include{scala}
\include{haskell}
\include{erlang}
\include{testdriven}
\include{factor}
\include{future}

%%--------------------------------------
%% Bibliography (set the widest label)
%%--------------------------------------
\begin{thebibliography}{99}

% Example
\bibitem{latex}Helmut Kopka and Patrick W. Daly, \textsl{A Guide to
\LaTeX: Document Preparation for Beginners and Advanced Users} (Addison-Wesley, Reading, MA, 1999), 3rd. ed.

% Example
\bibitem{Heijmans}H. Heijmans and J. Goutsias. 
  ``Nonlinear Multiresolution Signal Decomposition Schemes--Part II: Morphological Wavelets.'' 
   \textsl{IEEE Transactions on Image Processing}, 2000.

% Full book on python usage for scripting
\bibitem{Langtangen}Hans Petter Langtangen.
  ``Python Scripting for Computational Science, Second Edition.''
  \textsl{Spring Berlin Heidelberg}, 2004, 2006.

\end{thebibliography}

\end{document}
%%--------------------------------------
%% End of document 
%%--------------------------------------
